---
title: Template Code
output: 
  html_document:
      theme:
        sandstone
---
<hr>  
# `r report`'s Bird and Tree Report
### This title is individualized by running through a vector to print each name.

<hr>  
#### Here we would put some information about who surveyed, how they surveyed, and when they surveyed. 
  - This brief introduction should refresh the stakeholder's memory about the project's purpose and relevance.
  
#### If we had pictures from these fictitious surveys in this dataset, then we could could use the `knitr` package to print them.
  
```{r picture, out.width = "800px", echo = FALSE, eval = FALSE, fig.align = "center"}
knitr::include_graphics("path_to_picutre_file"))
```
  - We advise using the `knitr` package when printing pictures since if/else statements can be given if you wish to print certain pictures for certain stakeholders.

<hr>  

## Next, you can include graphs that tell a clear story about the findings:

### Here is a plot that shows `r report`'s bird counts compared to the average across towns.  
```{r bird, echo = FALSE, fig.align = "center"}
plot(bird_plot)
```
  
After printing the graph, you can give a short explanation, if necessary. Additional plots can be included as requested by the stakeholder or if they help clarify the overall "story" of the report.

<br>
<br>

### Here is a plot that shows `r report`'s tree counts compared to the average across towns. 
```{r tree, ech  = FALSE, fig.align = "center"}
plot(tree_plot)
```

<br>
<br>

### Here is a plot that shows how bird observations correlates with the number of trees in a park.
```{r bird_tree relationship, echo = FALSE, fig.align = "center", message = FALSE}
plot(birds_by_trees)
```
Each point represents a the number of birds observed each day by the number of trees in a park. We've added a trendline to show the **_positive_** relationship between the number of trees in a park and the number of birds observed in the park.   
  
  
<hr>  

#### Here we may give a brief summary and additional information to learn more.
  
  
#### Finally, we will link to a feedback form or provide instructions with contact information for how to provide feedback as well as any other unanswered stakeholder questions.
